[Re] Marriage and happiness: Providing evidence against a relationship between inequality and happiness in Oishi, Kesebir, and Diener (2011)

### 2020-02-20 analysis/paper.Rmd
metadata.yaml replaced, abstract added to report and yaml

>>>>

The purpose of the following paper is to do a replication of the paper "Marriage and happiness: Providing evidence against a relationship between inequality and happiness in Oishi, Kesebir, and Diener (2011)" [@marriagehappiness]. There is a crisis of reproducibility and replication in data science field. This paper follows the ReScience method of replicating a research paper to further validate the results of the paper. This particular replication is unique, because the paper being replicated is actually an alternate implementation of another paper, "Income Inequality and Happiness" [@incomeinequality]. While the first paper draws a connection between happiness and income, the second paper calls in the question the data used for this conclusion, and pulls in additional data for analysis. This second analysis, focused more on marriage and happiness is what this paper seeks to replicate.
